---
title: "Introduction to vswift"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vswift}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Import **vswift** into the current R session
```{r setup}
library(vswift)

# Display documentation for the 'vswift' package
help(package = "vswift")
```

```

The main function of the **vswift** package is `classCV`
```{r}
# Perform a train-test split with an 80% training set using LDA

result1 <- classCV(data = iris, target = "Species", 
                   split = 0.8, model_type = "lda", random_seed = 123)

# Perform a train-test split with five folds using stratified sampling with K-Nearest Neighbors while also specifying an additional argument for knn to specify the number of neighbors to consider

result2 <- classCV(data = iris, target = "Species", 
                   n_folds = 5, model_type = "knn", ks = 5, random_seed = 123)

#Perform a train-test split with an 80% training set and five folds with stratified sampling LDA and knn. Also specify an argument for knn and save the models for lda and knn.

args <- list("knn" = list(ks=5))
result3 <- classCV(data = iris, target = "Species", 
                   split = 0.8, n_folds = 5, model_type = c("lda", "knn"),
                   save_models = TRUE, mod_args = args)

```

You can also output specific results using the *print* function
```{r}

print(result3, model_type = "knn")
```

You can also output specific results using the *plot* function
```{r}

plot(result3, model_type = "knn", split = FALSE, cv = TRUE, class_names = c("setosa", "virginica"), metrics = "precision")

```

