---
title: "Introduction to vswift"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vswift}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Import **vswift** into the current R session
```{r setup}
library(vswift)

# Display documentation for the 'vswift' package
help(package = "vswift")
```

```

The main function of the **vswift** package is `classCV`
```{r}
# Perform a train-test split with an 80% training set using LDA

result1 <- classCV(data = iris, target = "Species",
                  train_params = list("split" = 0.8, "random_seed" = 50),
                  models = "lda")

# Perform a train-test split with five folds using stratified sampling with K-Nearest Neighbors while also specifying an additional argument for knn to specify the number of neighbors to consider
result2 <- classCV(data = iris, formula = Species ~ .,
                  train_params = list(split = 0.8, n_folds = 5, stratified = TRUE, random_seed = 50),
                  models = "knn",  ks = 5)

#Perform a train-test split with an 80% training set and five folds with stratified sampling LDA and knn. Also specify an argument for knn and save the models for lda and knn.

args <- list("knn" = list(ks=5))
result3 <- classCV(data = iris, formula = Species ~ .,
                  train_params = list(split = 0.8, n_folds = 5, stratified = TRUE, random_seed = 50),
                  models = c("lda", "knn"),  model_params = list(map_args = args))

```

You can also output specific results using the *print* function
```{r}

print(result3, models = "knn")
```

You can also output specific results using the *plot* function
```{r}

plot(result3, models = "knn", split = FALSE, cv = TRUE, class_names = c("setosa", "virginica"), metrics = "precision")

```

