---
title: "Introduction to vswift"
author: "Donisha Smith"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_width: 8
    fig_height: 6
vignette: >
  %\VignetteIndexEntry{Introduction to vswift}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


### Import **vswift** into the current R session.
```{r setup}
library(vswift)

# Display documentation for the 'vswift' package
help(package = "vswift")
```


### The main function of the **vswift** package is `classCV`.
```{r}
result1 <- classCV(
  data = iris, target = "Species",
  train_params = list("split" = 0.8, "random_seed" = 123),
  models = "lda"
)

# Perform a train-test split with five folds using stratified sampling with K-Nearest Neighbors while also specifying an additional argument for knn to specify the number of neighbors to consider
result2 <- classCV(
  data = iris, formula = Species ~ .,
  train_params = list(split = 0.8, n_folds = 5, stratified = TRUE, random_seed = 123),
  models = "knn",
  ks = 5
)

# Perform a train-test split with an 80% training set and five folds with stratified sampling LDA and knn. Also specify an argument for knn and save the models for lda and knn.

args <- list("knn" = list(ks = 5))

result3 <- classCV(
  data = iris, formula = Species ~ .,
  train_params = list(split = 0.8, n_folds = 5, stratified = TRUE, random_seed = 123),
  models = c("lda", "knn"),
  model_params = list(map_args = args)
)
```

### `print` can be used to produce command-line output of the performance metrics.
```{r}
print(result3, models = "knn")
```


### `plot` function can be used to visualize performance metrics.
```{r}
plot(result3, models = "knn", split = FALSE, cv = TRUE, class_names = c("setosa", "virginica"), metrics = "precision")
```

### `rocCurve`` can be used to generate ROC curves and ROC-AUC scores for binary classification targets. The model and preprocessed dataset must be saved.
```{r}
data <- iris
data$Species <- ifelse(data$Species == "setosa", "setosa", "not setosa")

result <- classCV(
  data = data, formula = Species ~ .,
  train_params = list(split = 0.8, n_folds = 5, stratified = TRUE, random_seed = 123),
  models = c("decisiontree", "randomforest"),
  model_params = list(map_args = args),
  save = list(models = TRUE)
)

output <- rocCurve(result, data)
```
